\setchapterpreamble[u]{\margintoc}
\chapter{Margin Stuff}

Sidenotes are a distinctive feature of all 1.5-column-layout books. 
Indeed, having wide margins means that some material can be displayed 
there. We use margins for all kind of stuff: sidenotes, marginnotes, 
small tables of contents, citations, and, why not?, special boxes and 
environments.

\section{请给我一个 Side note 的例子}

边界笔记，就是我使用 kaobook 的利用，我想充分想利用页面，来使用我自己对这段
题目或代码的理解。
\Command{sidenote\{Text of the note\}}. You can specify a 
mark\sidenote[O]{This sidenote has a special mark, a big O!} with \\ 
\Command{sidenote[mark]\{Text\}}, but you can also specify an offset, 
which moves the sidenote upwards or downwards, so that the full syntax is:

\begin{lstlisting}[style=kaolstplain]
\sidenote[mark][offset]{Text}
\end{lstlisting}

If you use an offset, you always have to add the brackets for the mark, 
but they can be empty.\sidenote{If you want to know more about the usage 
of the \Command{sidenote} command, read the documentation of the 
\Package{sidenotes} package.}

In \Class{kaobook} we copied a feature from the \Package{snotez} 
package: the possibility to specify a multiple of \Command{baselineskip} 
as an offset. For example, if you want to enter a sidenote with the 
normal mark and move it upwards one line, type:

\begin{lstlisting}[style=kaolstplain]
\sidenote[][*-1]{Text of the sidenote.}
\end{lstlisting}

As we said, sidenotes are handled through the \Package{sidenotes} 
package, which in turn relies on the \Package{marginnote} package.

\section{请给我一个 margin note 的例子}



This command is very similar to the previous one. You can create a 
marginnote with \Command{marginnote[offset]\{Text\}}, where the offset 
argument can be left out, or it can be a multiple of 
\Command{baselineskip},\marginnote[-1cm]{While the command for margin 
notes comes from the \Package{marginnote} package, it has been redefined 
in order to change the position of the optional offset argument, which 
now precedes the text of the note, whereas in the original version it 
was at the end. We have also added the possibility to use a multiple of 
\Command{baselineskip}  比如 \Command{marginnote[offset]\{你会是个好人，我猪声家教\}} 
as offset. These things were made only to make 
everything more consistent, so that you have to remember less things!} 
\eg

\begin{lstlisting}[style=kaolstplain]
\marginnote[-12pt]{Text} or \marginnote[*-3]{Text}
\end{lstlisting}

\begin{kaobox}[title=To Do]
A small thing that needs to be done is to renew the \Command{sidenote} 
command so that it takes only one optional argument, the offset. The 
special mark argument can go somewhere else. In other words, we want the 
syntax of \Command{sidenote} to resemble that of \Command{marginnote}.
\end{kaobox}

We load the packages \Package{marginnote}, \Package{marginfix} and 
\Package{placeins}. Since \Package{sidenotes} uses \Package{marginnote}, 
what we said for marginnotes is also valid for sidenotes. Side- and 
margin- notes are shifted slightly upwards 
(\Command{renewcommand\{\textbackslash marginnotevadjust\}\{3pt\}}) in 
order to align them to the bottom of the line of text where the note is 
issued. Importantly, both sidenotes and marginnotes are defined as 
floating if the optional argument (\ie the vertical offset) is left 
blank, but if the offset is specified they are not floating. Recall that 
floats cannot be nested, so in some rare cases you may encounter errors 
about lost floats; in those cases, remember that sidenotes and 
marginnotes are floats. To solve the problem, it may be possible to 
transform them into non-floating elements by specifying an offset of 
0pt.

\section{Footnotes}

Even though they are not displayed in the margin, we will discuss about 
footnotes here, since sidenotes are mainly intended to be a replacement 
of them. Footnotes force the reader to constantly move from one area of 
the page to the other. Arguably, marginnotes solve this issue, so you 
should not use footnotes. Nevertheless, for completeness, we have left 
the standard command \Command{footnote}, just in case you want to put a 
footnote once in a while.\footnote{And this is how they look like. 
Notice that in the PDF file there is a back reference to the text; 
pretty cool, uh?}

\section{Margintoc}

Since we are talking about margins, we introduce here the 
\Command{margintoc} command, which allows one to put small table of 
contents in the margin. Like other commands we have discussed, 
\Command{margintoc} accepts a parameter for the vertical offset, like 
so: \Command{margintoc[offset]}.

The command can be used in any point of the document, but we think it 
makes sense to use it just at the beginning of chapters or parts. In 
this document I make use of a \KOMAScript\xspace feature and put it in 
the chapter preamble, with the following code:

\marginnote{The font used in the margintoc is the same as the one for 
	the chapter entries in the main table of contents at the beginning 
	of the document.}

\begin{lstlisting}[style=kaolstplain]
\setchapterpreamble[u]{\margintoc}
\chapter{Chapter title}
\end{lstlisting}

As the space in the margin is a valuable resource, there is the 
possibility to print a shorter version of the title in the margin toc. 
Thus, there are in total three possible versions for the title of a
\marginnote{4．如果两个角的差的绝对值等于90°，就称这两个角互为垂角，例如:∠1＝120°，∠2＝30，|∠1－∠2|＝90°，则∠1和∠2互为垂角(本题中所有角都是指大于0°且小于180°的角)
（1）如图1，O为直线AB上的一点，∠AOC＝90°，∠EOD＝90°，直接指出图中所有互为余角的角，所有互为垂角的角；
（2）如果一个角的垂角等于这个角的补角的，求这个角的度数；  }
section (or subsection): the one for the main text, the one for the main 
table of contents, and the one for the margintoc. These versions can be 
specified at the same time when the section is created in the source 
\TeX file:
\begin{lstlisting}[style=kaolstplain]
\section[alternative-title-for-toc]{title-as-written-in-text}[alternative-title-for-margintoc]
\end{lstlisting}

By default, the margintoc includes sections and subsections.
If you only want to show sections, add
\begin{lstlisting}[style=kaolstplain]
\setcounter{margintocdepth}{\sectiontocdepth}
\end{lstlisting}
somewhere in your preamble.

\section{Marginlisting}

在“用托盘天平测量物质质量”实验中，应先将天平放在水平桌面上，然后将_____调节到；
标尺的“0”刻度处，发现指针左右摆动幅度如图甲所示，这时要将_____向_____（选“左”或“右”）移动，使天
平平衡。若将物体放在天平的左盘，当右盘中有砝码50克，5克的各1个，10克的2个，游码位置如图乙所示，则
被测物体的质量为_____。被使用的砝码中有因长久使用而被磨损的，那么被测物体的实际质量_____（
选“大于”或“小于”）测量值。
\Environment{marginlisting}. The support for this feature is still 
limited, especially for the captions, but you can try the following 
code:

\begin{marginlisting}
	\caption{An example of a margin listing.}
	\begin{lstlisting}[language=Python,style=kaolstplain]
print("Hello World!")
	\end{lstlisting}
\end{marginlisting}

\begin{verbatim}
\begin{marginlisting}
	\caption{My caption}
	\begin{lstlisting}[language=Python,style=kaolstplain]
	... code ...
	\end{lstlisting}
\end{marginlisting}
\end{verbatim}

Since we are here, let me spend a few words about listsings. Thanks to contributions from \href{https://github.com/fmarotta/kaobook/pull/225}{Kazuhiko Sakaguchi}, kaobook now supports both \Package{listings} and \Package{minted}. Just pass the option \Option{listing=listings} or \Option{listing=minted} when you load the \Class{kaobook} class, and the appropriate pacakge will be loaded.

Not only textual stuff can be displayed in the margin, but also figures. 
Those will be the focus of the next chapter.
